Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-03-17 Scripts/Initial_Analysis.Rmd
FIugres modiff.

dashed_lines <- tibble(
  x = c(2030,2050,2080),
  label = c("UN 2030 Agenda","Early range shift  ","Late range shift   ")
)

@@

count_eez_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 40,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative number of EEZs",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Year of range shift",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(legend.position = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.1
  )

#### Count stock plot 
count_stock_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 750,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative number of stocks",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p(leg_pos = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.7, 
                     end = 0.7
  )

# Percentage plot
percentage_plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  geom_area(data = subset(plot_data, level == "stock" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 18,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative proportion of the total (%)",
                     expand = c(0,0)
  ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p(leg_pos = "right") +
  theme(
    strip.text.x = element_blank()
  ) +
  guides(fill=guide_legend(title= "", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  )

@@

# Draw figure
  plot_all <- ggdraw() +
    # Latin America and the Car.
    draw_plot(count_stock_plot, x = 0.01, y = 0, width = 0.28, height = 0.90) +
    # Europe
    draw_plot(count_eez_plot, x = 0.28, y = 0, width = 0.28, height = 0.90) +
    # Percentage plot
    draw_plot(percentage_plot, x = 0.56, y = 0 , width = 0.28, height = 0.90) +
    # legend
    draw_plot(legend, x = 0.77, y = 0 , width = 0.28, height = 1) +
    # Labels
    draw_plot_label(label = c("A", "B","C"), 
                    size = 20,
                    x = c(0.01, 0.285,0.56), 
                    y = c(1,1,1)
    )

@@

# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
for(i in 1:2){

  tresh_list <- c("tresh_one","tresh_two")
  name_save <- paste("./Figures/emer_map_lat_",tresh_list[i],".png",sep = "")

@@

  boxplot_data <- Eme_Res %>% 
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>% 
    summarise(order = median(emerging_yr)) %>% 
    left_join(Eme_Res) %>% 
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>% 
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    )
    )

@@

  boxplot <- ggplot(boxplot_data) +
    geom_violin(
      aes(
        x = reorder(un_sub_region,order),
        y = emerging_yr
      ),
      fill = "grey"
    ) + 
    facet_wrap(~un_geo_region,
               scales = "free_x",
               nrow = 1) +
    # Median points
    geom_point(
      aes(
        x = reorder(un_sub_region,order),
        y = med,
        colour = med
      ),
      size = 5
    ) + 
    # h line
    geom_hline(yintercept = 2030, color = "grey", size = 0.5, linetype="dashed") +
    scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","",""),
                       direction = -1
    ) +
    xlab("") +
    ylab("Year of range shift") +
    scale_y_continuous(
                   labels = c(2000,2025, 2050, 2075, ">2100"), # not inluding the > because we dont know
    ) +
    my_ggtheme_p() +
    theme(
      axis.text.x = element_text(size = 16, angle = 45, face = "plain", hjust = 1), 
      strip.text.x = element_text(size = 18, colour = "black"), 
      axis.title.y = element_text(size = 18),
      axis.text.y = element_text(size = 16), 
      # axis.ticks.x = element_blank(),
      legend.position = ""
    )

>>>>

dashed_lines <- tibble(
  x = c(2030,2050,2070),
  label = c("UN 2030 Agenda","Mid range shift   ","Late range shift   ")
)

@@

count_eez_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 40,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative number of EEZs",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Year of range shift",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100")
  ) +
  my_ggtheme_p() +
  theme(legend.position = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.1
  )

#### Count stock plot 
count_stock_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 750,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative number of stocks",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100")
  ) +
  my_ggtheme_p(leg_pos = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.7, 
                     end = 0.7
  )

# Percentage plot
percentage_plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  geom_area(data = subset(plot_data, level == "stock" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  # Add dashed lines and labels
  geom_vline(
    data = dashed_lines,
    aes(
      xintercept = x
    ),
     linetype="dashed",
    color = "grey"
  ) +
  geom_text(data = dashed_lines,
            aes(
              x = x-4,
              y = 18,
              label = label
            ),
            size = 4,
            color = "white",
            angle = 90
  ) +
  scale_y_continuous("Cumulative proportion of the total (%)",
                     expand = c(0,0)
  ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100")
  ) +
  my_ggtheme_p(leg_pos = "right") +
  guides(fill=guide_legend(title= "", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1,
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  )

@@

# Draw figure
  plot_all <- ggdraw() +
    # Latin America and the Car.
    draw_plot(count_stock_plot, x = 0.01, y = 0, width = 0.29, height = 0.90) +
    # Europe
    draw_plot(count_eez_plot, x = 0.31, y = 0, width = 0.29, height = 0.90) +
    # Percentage plot
    draw_plot(percentage_plot, x = 0.61, y = 0 , width = 0.29, height = 0.90) +
    # legend
    draw_plot(legend, x = 0.84, y = 0 , width = 0.20, height = 1) +
    # Labels
    draw_plot_label(label = c("A", "B","C"), 
                    size = 20,
                    x = c(0.01, 0.285,0.56), 
                    y = c(1,1,1)
    )

@@

# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
tresh_list <- c("tresh_one","tresh_two")
for(i in 1:2){

  name_save <- paste("./Figures/emer_map_lat_",tresh_list[i],".png",sep = "")

@@

  # Weighted verion
  boxplot_data <- Eme_Res %>% 
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    mutate(weight = )
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    )#,
    # For number labels
    # un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

  # Non-weighted verion

  # boxplot_data <- Eme_Res %>% 
  #   # Get the order of boxes
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>%
  #   group_by(un_sub_region) %>% 
  #   summarise(order = median(emerging_yr),
  #             n_eezs = length(unique(sf_eez_name))) %>% 
  #   # Get the rest of the data
  #   left_join(Eme_Res) %>% 
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>% 
  #   mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
  #                                 ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
  #                                        ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
  #                                               paste(un_sub_region)))
  #   ),
  #   # For number labels
  #   un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
  #   )

@@

  boxplot <- ggplot(boxplot_data) +
    geom_violin(
      aes(
        x = reorder(un_sub_region,order),
        y = emerging_yr
      ),
      fill = "grey"
    ) + 
    facet_wrap(~un_geo_region,
               scales = "free_x",
               nrow = 1) +
    # Median points
    geom_point(
      aes(
        x = reorder(un_sub_region,order),
        y = med,
        colour = med
      ),
      size = 5
    ) + 
    # h line
    geom_hline(yintercept = 2030, color = "grey", size = 0.5, linetype="dashed") +
    scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","",""),
                       direction = -1
    ) +
    xlab("") +
    ylab("Year of range shift") +
    scale_y_continuous(
                   labels = c(2000,2025, 2050, 2075, ">2100"), # not inluding the > because we dont know
    ) +
    my_ggtheme_p() +
    theme(
      axis.text.x = element_text(size = 16, angle = 45, face = "plain", hjust = 1), 
      strip.text.x = element_text(size = 18, colour = "black"), 
      axis.title.y = element_text(size = 18),
      axis.text.y = element_text(size = 16), 
      # axis.ticks.x = element_blank(),
      legend.position = ""
    );boxplot
